\documentclass{article}

\usepackage[margin=1in]{geometry}
\usepackage{enumitem} 
\usepackage{tabularx}
\usepackage{hanging} % Hanging indents for citation
\usepackage{opensans} % Pretty fonts!

\renewcommand{\familydefault}{\sfdefault}
\setlength\parindent{0in} % Remove indents
\setlist[itemize]{topsep=3pt, itemsep=-1pt} % Change spacing in itemize
\pagenumbering{gobble} % Turn off page numbering

% Make ourselves a heading command
\newcommand{\heading}[1]
{
	\vspace{3pt}
	\textbf{#1} 
	\vspace{-6pt}
	
	\rule{\linewidth}{0.4pt}
}

\begin{document}
\begin{center}
{\Large\textbf{Greg d'Eon}}

\vspace{0.2cm}
Vancouver, BC ~ $\bullet$ ~ 
% (902) 293-9255 ~ $\bullet$ ~
greg.l.deon@gmail.com

\end{center}


\heading{Education}
\begin{center}
\begin{tabularx}{\textwidth}{Xr}
    \textbf{University of British Columbia} & Sept. 2019 -- present \\
    PhD in Computer Science \\
    Advisors: Kevin Leyton-Brown, James Wright (UAlberta) \\
    \\

	\textbf{University of Waterloo}	& Sept. 2017 -- Aug. 2019 \\
	Master's of Mathematics (Computer Science) \\
	Advisors: Edith Law, Kate Larson \\
% 	GPA: 98.25 / 100 \\
	\\
\end{tabularx}
\begin{tabularx}{\textwidth}{Xr}
	\textbf{Dalhousie University}	& Sept. 2012 -- Dec. 2016 \\
	Bachelor of Computer Engineering \\
% 	GPA (Bachelor, 2014-2016): 4.26 / 4.30  \\
% 	GPA (Diploma, 2012-2014): 4.30 / 4.30  \\
\end{tabularx}
\end{center}

\heading{Publications}
\begin{center}
\begin{tabularx}{\textwidth}{X}
\textbf{Preprints} \\
\hangpara{2em}{1}%
\textbf{Greg d'Eon}, Jason d'Eon, James R. Wright, and Kevin Leyton-Brown. ``The Spotlight: A General Method for Discovering Systematic Errors in Deep Learning.'' ArXiv, June 2021. \\\\

\textbf{Conference Papers} \\ 
\hangpara{2em}{1}%
\textbf{Greg d'Eon} and Kate Larson. ``Testing Axioms Against Human Reward Divisions in Cooperative Games.'' AAMAS 2020. \\\\

\hangpara{2em}{1}%
Blaine Lewis$^*$, \textbf{Greg d'Eon}$^*$, Andy Cockburn, and Daniel Vogel. ``KeyMap: Improving Keyboard Shortcut Vocabulary Using Norman's Mapping.'' CHI 2020. \\\\

\hangpara{2em}{1}%
Johann Wentzel, \textbf{Greg d'Eon}, and Daniel Vogel. ``Improving Virtual Reality Ergonomics through
Reach-Bounded Non-Linear Input Amplification.'' CHI 2020. \\\\

\hangpara{2em}{1}%
\textbf{Greg d'Eon}, Joslin Goh, Kate Larson, and Edith Law. ``Paying Crowd Workers for Collaborative Work.'' CSCW 2019. \\\\
\end{tabularx}

\begin{tabularx}{\textwidth}{X}
\textbf{Journal Papers} \\ 
\hangpara{1em}{1}%
Colin O'Flynn and \textbf{Greg d'Eon}. ``Power Analysis and Fault Attacks against Secure CAN: How Safe Are Your Keys?'' SAE International Journal of Transportation Cybersecurity and Privacy, 1.11-01-01-0001 (2018), 3-18. \\\\

\hangpara{1em}{1}%
Kathlyne Nelson, \textbf{Greg d'Eon}, Asher Wright, Lin Ma, Jian Xia, and Jeff Dahn. ``Studies of the effect of high voltage on the impedance and cycling performance of Li[Ni0.4 Mn0.4 Co0.2] O2/graphite lithium-ion pouch cells.'' Journal of The Electrochemical Society, 162.6 (2015), A1046-A1054. \\\\
\end{tabularx}

\begin{tabularx}{\textwidth}{X}
\textbf{Peer-Reviewed Workshop Papers} \\ 
\hangpara{1em}{1}%
\textbf{Greg d'Eon}, Kate Larson, and Edith Law. ``The Effects of Single-Player Coalitions on Reward Divisions in Cooperative Games.'' GAIW (Games, Agents, and Incentives Workshop) at AAMAS 2019.
\\\\
\end{tabularx}

\begin{tabularx}{\textwidth}{X}
\textbf{Non-Peer-Reviewed Publications} \\ 
\hangpara{1em}{1}%
Colin O'Flynn and \textbf{Greg d'Eon}. ``I, For One, Welcome Our New Power Analysis Overlords: An Introduction to ChipWhisperer-Lint'' (white paper). Black Hat USA, 2018. \\ \\
\end{tabularx}
\end{center}

\clearpage
\heading{Work Experience}
\begin{center}
\begin{tabularx}{\textwidth}{Xr}
	\textbf{NewAE Technology}		& Jan 2017 -- Aug 2017; May 2016 -- Aug 2016 \\
	Software Engineer
\end{tabularx}
\end{center}
\begin{itemize}
	\item Developed open-source software for the ChipWhisperer platform using Python, C, and Verilog, adding helpful software features and wide range of sample firmware.
	\item Wrote and revised a set of tutorials for the ChipWhisperer software, bringing the documentation up to date and increasing the value of the hardware.
    \item Taught in-person training courses with up to 30 students at Black Hat USA.
\end{itemize}

\begin{center}
\begin{tabularx}{\textwidth}{Xr}
	\textbf{Dalhousie University}	& Sept 2015 -- Dec 2015 \\
	Research Assistant with Dr. Guy Kember
\end{tabularx}
\end{center}
\begin{itemize}
	\item Created an analytical model for head impacts by working from existing published papers in acoustics.
	\item Implemented mathematical calculations and visualizations in Matlab and Mathematica, making calculations fast and efficient.
\end{itemize}

\begin{center}
\begin{tabularx}{\textwidth}{Xr}
	\textbf{Dalhousie University}	& 
	Jan 2014 -- Apr 2015; May 2014 -- Aug 2014 \\
	Research Assistant with Dr. Jeff Dahn
\end{tabularx}
\end{center}
\begin{itemize}
	\item Created an embedded system (hardware, firmware, and PC software) to emulate commercial lab equipment, providing an inexpensive method of data collection.
	\item Communicated effectively with graduate students and supervisors to create software with all desired features implemented.
	\item Designed and built a battery testing system, including a Visual Basic application and a custom sheet metal enclosure, allowing faster and more efficient data collection.
	\item Created an academic poster about the work and gave a talk to a small audience, including graduate students and undergraduate assistants from multiple labs.
\end{itemize}

\heading{Awards}
\begin{tabularx}{\textwidth}{X}
    Scholarships \\
\end{tabularx}
\begin{itemize}
\item 2019 NSERC CGS-D -- \$105,000 over 3 years
\item 2019 UBC 4-Year Fellowship -- \$72,800 over 4 years (declined to accept NSERC)
\item 2018 Ontario Graduate Scholarship -- \$15,000
\item 2018 Waterloo President's Graduate Scholarship -- \$5,000
\item 2017 NSERC CGS-M -- \$1,7500
\item 2017 Waterloo President's Graduate Scholarship -- \$10,000
% \item 2016 Dalhousie In-Course Scholarship -- \$2,000
\item 2014 John G.~Bruce Scholarship -- \$10,000 (renewed 2015)
% \item 2014 Walter~P.~Copp Memorial Prize -- \$400
\item 2012 Dalhousie Entrance Scholarship -- \$5,000 (renewed 2013 -- 2015)
\end{itemize}
\begin{tabularx}{\textwidth}{X}
    Distinctions \\
\end{tabularx}
\begin{itemize}
\item 2018 Distinguished Teaching Assistantship Award -- Waterloo Computer Science
\item 2017 Dalhousie University Medal -- Top Academic Standing, Computer Engineering
\item 2017 IEEE Atlantic Section Medal -- Top Academic Standing, Computer Engineering
\item 2014 Kenneth Marginson Award -- Top Academic Standing, Class of Engineering
\item 2014 Bob Walter Award -- Student Vote, Class of Engineering 
% \item 2012 Governor General's Award -- Top Academic Standing, Prince Andrew High
\end{itemize}

\clearpage

\heading{Teaching Experience}
\begin{center}
\begin{tabularx}{\textwidth}{Xr}
	\textbf{University of Waterloo}	&
	Sept. 2017 -- Aug. 2019 \\
	Teaching/Instructional Assistant
\end{tabularx}
\end{center}
\begin{itemize}
	\item Led lab sessions with up to 60 students, held office hours, and marked assignments/tests
	\item TA/IA duties:
	\begin{itemize}
	\item 
		\makebox[1.25in][l]{May - Aug. 2019:} 
		\makebox[2.5in][l]{Human-Computer Interaction} (CS449)
	\item 
		\makebox[1.25in][l]{Jan. - Apr. 2019:} 
		\makebox[2.5in][l]{Intro to Computer Programming 1} (CS105)
	\item 
		\makebox[1.25in][l]{Sept. - Dec. 2018:} 
		\makebox[2.5in][l]{Intro to Computer Programming 1} (CS105)
	\item 
		\makebox[1.25in][l]{May - Aug. 2018:} 
		\makebox[2.5in][l]{Human-Computer Interaction} (CS449)
	\item 
		\makebox[1.25in][l]{Jan. - Apr. 2018:} 
		\makebox[2.5in][l]{Intro to Computer Programming 2} (CS106)
	\item 
		\makebox[1.25in][l]{Sept. - Dec. 2017:} 
		\makebox[2.5in][l]{Intro to Computer Programming 1} (CS105)
	\end{itemize}
\end{itemize}

\begin{center}
\begin{tabularx}{\textwidth}{Xr}
	\textbf{Dalhousie University}	&
	Sept. 2013 -- Dec. 2016 \\
	Teaching Assistant
\end{tabularx}
\end{center}
\begin{itemize}
	\item Led weekly two-hour tutorial sessions, teaching up to 90 students by demonstrating examples and helping individual students as needed 
	\item Courses taught:
	\begin{itemize}
	\item 
		\makebox[1.25in][l]{Sept - Dec 2016:} 
		\makebox[1.25in][l]{C++ Programming} (ENGM3282)
	\item 
		\makebox[1.25in][l]{Sept - Dec 2015:} 
		\makebox[1.25in][l]{C Programming} (ENGM1081)
	\end{itemize}
	\item Graded up to 120 assignments or 100 tests each week for first-, second-, and third-year math courses, providing accurate marks and helpful comments to students.
	\item Courses graded:
	\begin{itemize}
	\item 
		\makebox[1in][l]{May  - Aug 2016:} 
		\makebox[1.5in][l]{Vector Calculus} (ENGM2101)
	\item 
		\makebox[1in][l]{Sept - Dec 2015:} 
		\makebox[1.5in][l]{C++ Programming} (ENGM3282)
	\item 
		\makebox[1in][l]{Sept - Dec 2015:} 
		\makebox[1.5in][l]{C Programming} (ENGM1081)
	\item 
		\makebox[1in][l]{Jan  - Apr 2015:} 
		\makebox[1.5in][l]{Differential Equations} (ENGM2022)
	\item 
		\makebox[1in][l]{Sept - Dec 2014:} 
		\makebox[1.5in][l]{Vector Calculus} (ENGM2101)
	\item 
		\makebox[1in][l]{Jan  - Apr 2014:} 
		\makebox[1.5in][l]{Linear Algebra} (ENGM1041)
	\item 
		\makebox[1in][l]{Sept - Dec 2013:} 
		\makebox[1.5in][l]{C Programming} (ENGM1081)
	\end{itemize}
\end{itemize}

\begin{tabularx}{\textwidth}{Xr}
	\textbf{Dalhousie University}	&
	Sept. 2013 -- May 2016 \\
	Private Tutor
\end{tabularx}
\begin{itemize}
	\item Tutored first- and second-year students in a variety of groups, ranging from individual tutoring to lecture-style discussions with 30 students
	\item Courses tutored include engineering physics, chemistry, design, and mathematics, with a heavy emphasis on Vector Calculus and Differential Equations
\end{itemize}

\clearpage

\heading{Extra-curricular Involvement}
\begin{center}
\begin{tabularx}{\textwidth}{Xr}
	\textbf{Formula SAE}	& 
	Sept 2013 -- May 2017 \\
	Dalhousie University
\end{tabularx}
\end{center}
\begin{itemize}
	\item May 2016 -- May 2017: Team captain
	\begin{itemize}
		\item Led 50+ students in a hierarchical team structure
		\item Responsible as the face of the team, directing meetings with system leads, working on recruitment and sponsorships, and upkeeping the team's social media
		\item Contributed heavily to multiple areas of the team, providing technical help to the suspension system and temporarily leading the powertrain system
	\end{itemize}
	\item Sept 2015 -- April 2016: Electrical system lead
	\begin{itemize}
		\item Led a group of 10 engineering students, managing tasks on tight deadlines
		\item Used professional engineering software to design and build wiring systems for a new engine, including work on an electronic shifter
	\end{itemize}
	\item Sept 2014 -- August 2015: Electrical system member
	\item Sept 2013 -- August 2014: Aerodynamics system member
\end{itemize} ~\\

% \heading{Academic Service}
% Reviewer for:
% \begin{itemize}
%     \item CHI 2018 (late-breaking work), 2019 (main track)
%     \item CSCW 2019
% \end{itemize}

% \heading{Hobbies and Community Involvement}
% \textbf{Running}
% \begin{itemize}
% 	\item Avid middle- and long-distance runner (2004 -- present)
% 	\item 2016 Natal Day 2 Miler: 5th place overall (11:28)
% 	\item 2015 Valley Harvest Half Marathon: 9th place overall (1:23:15)
% 	\item 2012 Nova Scotia Track \& Field Provincials: 1500m bronze medalist 
% \end{itemize}

% \textbf{Music}
% \begin{itemize}
% 	\item Drummer and singer for band \textit{Sunday Run} (2012 -- 2017)
% 	\item Played at several venues annually, including fundraisers for local elementary school, soup kitchen, and charities
% 	\item Proficient in music theory and arranging
% \end{itemize}

% \textbf{Volunteer Work}
% \begin{itemize}
% 	\item Volunteered as summer camp leader at Stevens Road Church (2009 -- 2013)
% 	\item Led up to 50 children aged 3-12 in arts/crafts and sports at full day camp
% \end{itemize}

\end{document}
